\documentclass{article}

\date{2021-11-2}
\title {The historical perspective of any 5 programming languages}
\author{OKOEDE KAROL}

\begin{document}
	\maketitle
	\newpage
	\section{JAVA programming language}
	\begin{itemize}
	 \item java programing language is one of the world most popular programming language. This language was created on the 23rd of january 1996 by sun microsystem link. The corporation was known for selling computers and their components. James Gosling the man that led the team of researchers to create java. Java has the ability to allow electronic devices comunicate with each other. This is why java programming is known as the king of programming.
	 \item Java has so many applications like business applications, cloud-based distribution, mobile application, web application and so much more.
	 \item Every programming language has their own integrated development environment (IDE). Java IDE is called Eclipse. Eclipse provide software developers with the instrument needed to create software swiftly and structured.
	 \item Java like many other languages possess related programming language. For JAVA its C++. Java is related to C++ because JAVA was created from the fundamentals of C++.
	\end{itemize}
\newpage
\section{Python programming language}
\begin{itemize}
	\item Python programming is one of the most fundamental and sort out high level programming language. This programming language was created in the year 1980 and was then released in february 1991 by Guido Van Rossum, a dutch programmer. Currently the version of python that is being run is python 3.0 which was released on descember 2008.
	\item Python being a high level programming language has so many application such as game development, web development, business application, machine learning, artificial intelligence and so on.
	\item IDLE is an integrated Development environment that is used by python programming language. IDLE is on of the simplest IDE there is.
	\item Python has related programming which are ABC language and Modula-3. . ABC language and Modula-3 are said to be the programming language that influenced python. 
\end{itemize}
\newpage
\section{PHP prograamming language}
\begin{itemize}
	\item PHP programming language is a script language and interpreter that  was created in the year 1994 but was released in the year 1995 by an man named Rasmus Lerdorf. PHP stands for Hypertext Preprocessor.
	\item Now PHP is now used by so many well known application such as Wikipedia, Facebook, Tumblr, Etsy and even WordPress.
	\item PHP has no designated IDE, that’s why we can uses both commercial and open source IDE packages. Examples are PHPstorm, Eclipse, NetBeans and so much more.
	\item PHP doesn’t really have a related program but when it comes to language syntax and keyboard, PHP is similar to C, C++, Java and perl.
	
\end{itemize}
\newpage
\section{JAVASCRIPT Programming language} 
\begin{itemize}
\item This is a text-based programming language that was created by a man named Brendan Eich in the year 1995. Fun fact, in the early years of javascript was originally called Mocha. The first version of javascript has so many great features like First-class object functions, Syntax which is very similar to Java and Prototype-based object model.
\item Javascript is used many applications because of its many features. Examples of the applications that use javascript are sublime text, bracket, notepad++ and so much more.
\item Javascript has its very own IDE which is called Codeanywhere which is a cloud based and crossed platform IDE that’s allows software developers write code write, change, and run web development projects directly from any web browser of their choice. 
\item Javascript programming language has related programming languages which are HTML and CSS languages.
 
\end{itemize}
\newpage
\section{COBOL programming language}
\begin{itemize}
	\item Cobol which stood for Common Business-Oriented Language  is a high level programming language that was created in the year 1959 by CODASYL which stood for  the Conference/Committee on Data Systems Languages. In its time Cobol was one of the most used programming language of its time.
	\item Cobol is a program that is manly used in business, finance and administrative applications and systems.  COBOL is still widely used in applications deployed on mainframe computers. 
	\item From my research I can say that cobol doesn’t have a designated integrated development environment and that why it uses more of  commercial or open source IDE.
	\item Cobol programming language has so many related programming languages, examples are python, java, javascript and C.
\end{itemize}

 
\end{document}